A Study on Common Bug Fix Patterns in Rust

### 2022-10-13 sections/methodology.tex
added labels to tikZs

@@

@@

@@

\begin{table}
\caption{\label{table:repos} Target repositories for mining}
\begin{tabular}{c|c|c|c|c}
    Project Name & Stars(k) & LOC & \# Commits & Avg. Code Churn \\ \hline
    denoland/deno & 84.7 & 562468 & 7730 & 49.22 \\ \hline
    tauri-apps/tauri & 48.5 & 130726 & 2929 & 31.67 \\ \hline
    alacritty/alacritty & 41.2 & 45803 & 2017 & 27.53 \\ \hline
    sharkdp/bat & 36.4 & 93258 & 2392 & 59.13 \\ \hline
    starship/starship & 28 & 176630 & 2290 & 25.1 \\ \hline
    rust-lang/rustlings & 28.7 & 9852 & 1391 & 8.92 \\ \hline
    meilisearch/meilisearch & 28.6 & 66872 & 3849 & 279.7 \\ \hline
    sharkdp/fd & 24.2 & 10383 & 1025 & 12.2 \\ \hline
    swc-project/swc & 23.5 & 13512766 & 5205 & 44.34 \\ \hline
    yewstack/yew & 23.2 & 112972 & 2239 & 21.79 \\ \hline
    xi-editor/xi-editor & 19.5 & 58783 & 2104 & 28.67 \\ \hline
    AppFlowy-IO/AppFlowy & 25.9 & 182830 & 2600 & 29.49 \\ \hline
    firecracker-microvm/firecracker & 18.9 & 156759 & 3536 & 58.26 \\ \hline
    nushell/nushell & 20.3 & 181710 & 5922 & 22.38 \\ \hline
    ogham/exa & 18.9 & 17114 & 1558 & 11.99 \\ \hline
    SergioBenitez/Rocket & 18.2 & 90055 & 2127 & 19.75 \\ \hline
    rustdesk/rustdesk & 27.7 & 85322 & 1664 & 72.81 \\ \hline
    tokio-rs/tokio & 17.2 & 126089 & 3006 & 28.87 
\end{tabular}
\end{table}

>>>>

    \node[draw, minimum height=0.5, fill=yellow!20] at (-0.74,1.7) {ASTDiff};

@@

        \node[draw, minimum height=0.5, fill=yellow!20] at (-0.74,1.7) {ASTDiff};

        \node[draw, minimum height=0.5, fill=yellow!20] at (4.29,1.73) {Occurrences data};

@@

        \node[draw, minimum height=0.5, fill=yellow!20] at (4.02,-0.25) {Weights data};

@@

\begin{table}
\caption{\label{table:repos} Target repositories for mining}
\begin{tabular}{l r r r r}
    Project Name & Stars(k) & LOC & \# Commits & Avg. Code Churn \\
    denoland/deno & 84.7 & 562468 & 7730 & 49.22 \\
    tauri-apps/tauri & 48.5 & 130726 & 2929 & 31.67 \\
    alacritty/alacritty & 41.2 & 45803 & 2017 & 27.53 \\
    sharkdp/bat & 36.4 & 93258 & 2392 & 59.13 \\
    starship/starship & 28 & 176630 & 2290 & 25.1 \\
    rust-lang/rustlings & 28.7 & 9852 & 1391 & 8.92 \\
    meilisearch/meilisearch & 28.6 & 66872 & 3849 & 279.7 \\
    sharkdp/fd & 24.2 & 10383 & 1025 & 12.2 \\
    swc-project/swc & 23.5 & 13512766 & 5205 & 44.34 \\
    yewstack/yew & 23.2 & 112972 & 2239 & 21.79 \\
    xi-editor/xi-editor & 19.5 & 58783 & 2104 & 28.67 \\
    AppFlowy-IO/AppFlowy & 25.9 & 182830 & 2600 & 29.49 \\
    firecracker-microvm/firecracker & 18.9 & 156759 & 3536 & 58.26 \\
    nushell/nushell & 20.3 & 181710 & 5922 & 22.38 \\
    ogham/exa & 18.9 & 17114 & 1558 & 11.99 \\
    SergioBenitez/Rocket & 18.2 & 90055 & 2127 & 19.75 \\
    rustdesk/rustdesk & 27.7 & 85322 & 1664 & 72.81 \\
    tokio-rs/tokio & 17.2 & 126089 & 3006 & 28.87 
\end{tabular}
\end{table}
